\section{Conclusion}\label{sec-conclude}

\yanyan{may shorten this to half the length.}
In this paper we introduced a new technology that can make it easier for 
researchers to take advantage of of the rich data gathering potential of 
portable devices, such as smartphones and tablets. Sensibility Testbed
directly addresses the twin challenges thathave stymied that potential in
the past: the very real risk such studies pose to the privacy
of the device owner, and the many difficulties researchers have in 
ensuring that data will be gathered in a responsible and ethical manner.
Designed to safely and securely run experiment code on Android devices,
Sensibility Testbed  eliminates the need for researchers to 
expend the time and energy to recruit participants or to settle
for a limited and non-representative pool of test candidates. It also automates
the process of implementing and enforcing any IRB policy designated by
their sponsoring institution, ensuring ethical behavior in the data 
gathering process withoutany added effort by the researcher. The latter is made possible
through precise programmable control of sensor access through the use of blurring
layers that substitute approximated data for the more intrusive raw data. By 
safeguarding the raw data acquired, and shutting off access to sensors that can
be especially intrusive to the privacy of device owners, Sensibility Testbed
greatly reduces the risk of participation for device owners thus encouraging greater
participation in such initiatives.

For researchers, Sensibility Testbed not only offers a larger and more diverse pool
of test subjects, but also simplifies both the application for, and implementation
of IRB policies for their deployed experiments. Other benefits include the ability to
run multiple experiments simultaneously on the same devices
at the same time with no cross-over between projects, as well as the opportunity to 
reuse experimental set-ups, and easily share data with other researchers.
 
Based on a study of the literature, Sensibility Testbed can protect device owners
from most of the security and privacy issuesidentified in previous projects
using mobile devices. Deployments of the testbed are currently underway and
additional information about the security effectiveness of the process will
be forthcoming in the months ahead.\lois{Not sure about this last sentence. 
Do we want to commit to any type of future action?}